---
title: "R Markdown in Quarto Report"
author: "AN Rwizard"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

You are reading a document created with Rmarkdown and rendered in Quarto. 

This document includes a mixture of text and code. \The code below is wrapped in back ticks and at render-time the code will be executed and the  result inserted into the document

```{r}
library(palmerpenguins)
x <- penguins$bill_length_mm
y <- penguins$bill_depth_mm

lm(y ~ x)
```

We can format any text using Markdown, simple inline text elements convey the formatting

## Hashes at the start of a line make it a heading.

Two hashes gives a Level 2 heading, three hashes a Level 3 heading. Headings go from Level 1 (biggest) to Level 6 (smallest)

We can create text formats including _italics_ and **bold**.

We can make lists:

  1. First item
  2. Second item
  
We can make hyperlinks [a link to Google](https://www.google.com)


The whole document acts as a single R session  - so objects created in earlier
blocks can be used later. 

Plots are inserted into the document.

Options for code blocks can be set at the top after a `#|` (a hash and a pipe).

```{r}
#| fig-width: 6
#| fig-cap: "A plot, yesterday."

plot(x,y)
```
